Alleviating the Topology Mismatch Problem in Distributed Overlay Networks

### 2015-05-17 unstructured.tex
2015.05.16 (Alex & Vassilis) Extensive re-wording throughout the paper. Abstract on its one file. Better figure scaling and alignment. Re-ordering of algorithms in the histogram figures to match paper order of appearence and the table ordering.

As a methodology, topology adaptation, ultimately aims to reduce the 
average path traversing cost from one node to another.
In doing so, the methodology re-arranges the
overlay network so that it becomes a better fit 
for the underlying \emph{IP} network
as Figure~\ref{figure:topology-adaptation} depicts.
Despite the fact that the above is a plausible proposition,
it is not always advantageous though. For example, a topology adaptive
algorithm can exchange a slow edge in the overlay with a faster one
thus reducing the average latency of the network communication.
The pitfall here is that this new virtual link
can traverse a fast \emph{AS}--to--\emph{AS} link meaning that even though
message round-trip-time is reduced, it has actually additional cost in terms of
inter-\emph{ISP} communication accounting and management.
%%
\begin{figure}[ht]
\centering
\subfigure[Inefficient overlay topology averaging $\simeq 16$ delay units.] {
  \includegraphics[scale=0.4]{img/pdf/topology-adaptation-before.pdf}
  \label{figure:topology-adaptation:before}
}\qquad\qquad
\subfigure[Efficient overlay topology after adaptation averaging $\simeq 11$ delay units.] {
  \includegraphics[scale=0.4]{img/pdf/topology-adaptation-after.pdf}
  \label{figure:topology-adaptation:after}
}
\caption{A simplified example on how overlay topology adaptation may improve matters.}
\label{figure:topology-adaptation}
\end{figure}
%%

@@

Figure~\ref{figure:forwarding-optimisation} shows a simple example
of how forwarding optimization may work.
%%
\begin{figure}[ht]
\centering
\subfigure[Typical blind flooding.] {
\includegraphics[scale=0.20]{img/pdf/forwarding-optimization-before.pdf}
  \label{figure:forwarding-optimisation:before}
}\qquad\qquad
\subfigure[A node can decide where to forward the messages.] {
  \includegraphics[scale=0.20]{img/pdf/forwarding-optimization-after.pdf}
  \label{figure:forwarding-optimisation:after}
}
\caption{Forwarding optimization in constraining message flooding.}
\label{figure:forwarding-optimisation}
\end{figure}
%%
Fig.~\ref{figure:forwarding-optimisation:before} 
shows a protocol that simply floods the entire network 
in search of object found in the nodes colored in black.
Alternatively, a node can decide to forward its
messages not to every output link but to a specific 
or subset of its outgoing links.
In Fig.~\ref{figure:forwarding-optimisation:after}, 
the node in the middle, does not flood its neighbors as instead 
in only picks one of them.
The dashed line on the right, shows that, 
for this routing process, the protocol has
rendered two potential forwarding paths as inefficient (e.g., the target nodes
show overloading signs).

@@

Caching is widely used to exploit locality and minimize redundant
transfer of data. Caching has with much success been successfully 
adopted by web-- and file--server application environments. 
Since peers in a \p\ system also operate as servers,
it is intuitively expected that \p\ file--sharing systems can also benefit from
caching in improving performance and reducing overall resource usage. 
However, the design of caches in this context 
is non-trivial compared to the web-based caching. 
Due to the fact nodes play the double role of server and client,
two important issues have to be considered at design time. 
First, the lifetime of a query is short, as the nodes join 
and leave frequently. Second, the result
of a single query string is not always the same, as this depends on the
source of the query, the \emph{TTL} value set for the messages, 
the current interconnection of peers and the 
high volatility of the environment. 
Thus, to develop a successful caching system for a \p\ architecture, these
parameters also have to be carefully considered. 
\p\ caching/replication can be applied
at two different levels, namely caching indices or pointers to data 
(Fig.~\ref{figure:replication:index}) or caching the data itself 
(Fig.~\ref{figure:replication:data}). 
%%%
\begin{figure}[ht]
\centering
\subfigure[Indexing can reduce the cost of the last hop.] {
\includegraphics[scale=0.3]{img/pdf/replication-index.pdf}
  \label{figure:replication:index}
}\qquad\qquad
\subfigure[Data replication along the path of a successful query.] {
  \includegraphics[scale=0.3]{img/pdf/replication-data.pdf}
  \label{figure:replication:data}
}
\caption{Index and data replication strategies.}
\label{figure:replication}
\end{figure}
%%
Successful implementations have
already been developed in some commercial \p\ systems, like 
\emph{KaZaA} or less popular ones including \emph{Gia} and \emph{BNS}.
%%%
Even though the state of the art in \p\ protocols using caching methods
helps reduce the burden of network resources, 
their contribution in addressing the actual mismatch between the overlay and
and the underlying networks remains limited.

@@

In landmark-based algorithms, nodes use network delay (e.g., \emph{RTT}) as a
distance measurement method to position themselves with respect to ``a priori''
known servers on the Internet, like \emph{Ono} which uses the \emph{CDN}-infrastructure
for this purpose.
These landmark--servers are used by nodes to estimate 
their positions based on the intuitive assumption that nodes
with similar distances to a set of landmarks, are physically close to each
other, as well, over the network. 
In Figure~\ref{figure:landmarking}, the newly
arriving peer, measures its distance to an array of landmark point denoted as
$L_n$ and and makes a sorted list of the peers, say in increasing order. Then in
order to choose the already participating peers with which to connect to,
the peer compares its list to the list of the potential neighbor. Peers with similar
measured distances to the these landmark points are likely to be close to
each other as well.
%%
\begin{figure}[ht]
\centering
  \includegraphics[scale=0.4]{img/pdf/landmarking.pdf}
\caption{Landmark binning during node bootstrap.}
\label{figure:landmarking}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{unstructured-table}

\input{unstructured-plot}

>>>>

As a methodology, topology adaptation, ultimately aims to reduce the 
average path traversing cost from one node to another.
In doing so, the methodology re-arranges the
overlay network so that it becomes a better fit 
for the underlying \emph{IP} network
as Figure~\ref{figure:topology-adaptation} depicts.
Despite the fact that the above is a plausible proposition,
it is not always advantageous though. For example, a topology adaptive
algorithm can exchange a slow edge in the overlay with a faster one
thus reducing the average latency of the network communication.
The pitfall here is that this new virtual link
can traverse a fast \emph{AS}--to--\emph{AS} link meaning that even though
message round-trip-time is reduced, it has actually additional cost in terms of
inter-\emph{ISP} communication accounting and management.
%%
\begin{figure}[ht]
\centering
\subfigure[Inefficient overlay topology averaging $\simeq 16$ delay units.] {
  \includegraphics[scale=0.36]{img/pdf/topology-adaptation-before.pdf}
  \label{figure:topology-adaptation:before}
}\qquad\qquad
\subfigure[Efficient overlay topology after adaptation averaging $\simeq 11$ delay units.] {
  \includegraphics[scale=0.36]{img/pdf/topology-adaptation-after.pdf}
  \label{figure:topology-adaptation:after}
}
\caption{A simplified example on how overlay topology adaptation may improve matters.}
\label{figure:topology-adaptation}
\end{figure}
%%

@@

Figure~\ref{figure:forwarding-optimisation} shows a simple example
of how forwarding optimization may work.
%%
\begin{figure}[ht]
\centering
\subfigure[Typical blind flooding.] {
\includegraphics[scale=0.17]{img/pdf/forwarding-optimization-before.pdf}
  \label{figure:forwarding-optimisation:before}
}\qquad\qquad
\subfigure[A node can decide where to forward the messages.] {
  \includegraphics[scale=0.19]{img/pdf/forwarding-optimization-after.pdf}
  \label{figure:forwarding-optimisation:after}
}
\caption{Forwarding optimization in constraining message flooding.}
\label{figure:forwarding-optimisation}
\end{figure}
%%
Fig.~\ref{figure:forwarding-optimisation:before} 
shows a protocol that simply floods the entire network 
in search of object found in the nodes colored in black.
Alternatively, a node can decide to forward its
messages not to every output link but to a specific 
or subset of its outgoing links.
In Fig.~\ref{figure:forwarding-optimisation:after}, 
the node in the middle, does not flood its neighbors as instead 
in only picks one of them.
The dashed line on the right, shows that, 
for this routing process, the protocol has
rendered two potential forwarding paths as inefficient (e.g., the target nodes
show overloading signs).

@@

Caching is widely used to exploit locality and minimize redundant
transfer of data. Caching has with much success been successfully 
adopted by web-- and file--server application environments. 
Since peers in a \p\ system also operate as servers,
it is intuitively expected that \p\ file--sharing systems can also benefit from
caching in improving performance and reducing overall resource usage. 
However, the design of caches in this context 
is non-trivial compared to the web-based caching. 
Due to the fact nodes play the double role of server and client,
two important issues have to be considered at design time. 
First, the lifetime of a query is short, as the nodes join 
and leave frequently. Second, the result
of a single query string is not always the same, as this depends on the
source of the query, the \emph{TTL} value set for the messages, 
the current interconnection of peers and the 
high volatility of the environment. 
Thus, to develop a successful caching system for a \p\ architecture, these
parameters also have to be carefully considered. 
\p\ caching/replication can be applied
at two different levels, namely caching indices or pointers to data 
(Fig.~\ref{figure:replication:index}) or caching the data itself 
(Fig.~\ref{figure:replication:data}). 
%%%
\begin{figure}[ht]
\centering
\subfigure[Indexing can reduce the cost of the last hop.] {
\includegraphics[scale=0.25]{img/pdf/replication-index.pdf}
  \label{figure:replication:index}
}\qquad\qquad
\subfigure[Data replication along the path of a successful query.] {
  \includegraphics[scale=0.25]{img/pdf/replication-data.pdf}
  \label{figure:replication:data}
}
\caption{Index and data replication strategies.}
\label{figure:replication}
\end{figure}
%%
Successful implementations have
already been developed in some commercial \p\ systems, like 
\emph{KaZaA} or less popular ones including \emph{Gia} and \emph{BNS}.
%%%
Even though the state of the art in \p\ protocols using caching methods
helps reduce the burden of network resources, 
their contribution in addressing the actual mismatch between the overlay and
and the underlying networks remains limited.

@@

In landmark-based algorithms, nodes use network delay (e.g., \emph{RTT}) as a
distance measurement method to position themselves with respect to ``a priori''
known servers on the Internet, like \emph{Ono} which uses the \emph{CDN}-infrastructure
for this purpose.
These landmark--servers are used by nodes to estimate 
their positions based on the intuitive assumption that nodes
with similar distances to a set of landmarks, are physically close to each
other, as well, over the network. 
In Figure~\ref{figure:landmarking}, the newly
arriving peer, measures its distance to an array of landmark point denoted as
$L_n$ and and makes a sorted list of the peers, say in increasing order. Then in
order to choose the already participating peers with which to connect to,
the peer compares its list to the list of the potential neighbor. Peers with similar
measured distances to the these landmark points are likely to be close to
each other as well.
%%
\begin{figure}[ht]
\centering
  \includegraphics[scale=0.35]{img/pdf/landmarking.pdf}
\caption{Landmark binning during node bootstrap.}
\label{figure:landmarking}
\end{figure}

\input{unstructured-table}
\input{unstructured-plot}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
